### 2019-06-14 thesis-template/msc-thesis.tex
update

This chapter will summarize the main contributions of this work studied and state targeted aims and goals as a first step in sect. \ref{sec:overview}. Then we will have a short introduction to the implemented global illumination scheme derived and simplified from an nVidia global illumination approach in sect. \ref{sec:scheme}. Last, we will state the effectively implemented Visualization methods Light Transport Visualization and Global Illumination gradient proposed as innovatively invented tensor visualization techniques.

@@

\section{Requirements and Ambitions}
\label{sec:spec} 
Our ambition is to motivate a simple and efficient global illumination propagation scheme able to distribute energy profiles in discrete polar form in 2D/3D-space w.r.t. energy conservation and propagation attenuation principles. We then generate transmission profiles from the eigensystems (principal component frames) of the tensors for each cell in the domain (field). This step is done, to provide an orientation for a grid of crystal fibre structures (cf. optical fibres) to redirect the intensities in analogy to the anisotropies of the tensor field within a glyph representation, obtained from Principal Component Analysis. Our approach should be implicitly adaptive to any kind of 2D dataset or slices of 3D datasets. Thus, we require to be compatible to handle any kind of matrix (symm./anti-symm.) and any kind of resolution of the field (full-spectrum). At last, our ambition is to segment key locations (LCS/ridges) in the field with tensor field lines (hyperstreamlines) converging/diverging, which is necessarily the same (for bidirectional eigenvectors of tensors). Thus, we aim to generate a new FTLE-related method for tensor field visualization by applying a light transport gradient to the resulting light distributions for every possible position and direction of the light source in the grid generated by stimulation with Delta-pulses. Our approach should efficiently handle (relatively) large datasets with reasonable resolutions. 
%Knapp zwei Seiten, in dem die Anforderungen, die Zielsetzung und die
%Methoden überblicksartig beschrieben werden. Hier sollte die
%Beschreibung ``technischer'' bzw.~``formaler'' sein als in der
%Einleitung, da der Leser nun mit den Grundlagen und verwandten
%Arbeiten vertraut ist.

\section{Light Transport (Propagation) Scheme}
\label{sec:scheme}
Within the scope of this work, we will motivate a light transport propagation scheme designed to efficiently propagate initial intensity profiles stored in polar coordinates given as symbolic impulses (stimuli) by the user or the config. This polar profiles are first sampled into a vector with elements ranging over the interval $[0,2\pi]$. Polar profiles for different light sources are shown in Fig. \ref{polar}:
\begin{figure}[!t]
  \centering
 {
    \includegraphics[width=0.8\textwidth]
    {img/strahler.png}
  }
  \caption{Polar profiles for different types of emitters ($m=0$: spherical emitter, $m=1$: Lambert emitter, $m=2$: cone emitter}
  \captionsetup{font={footnotesize,bf,it}}
  \caption*{src: \url{http://www.optik.uni-erlangen.de/odem/vorlesung/ws1213/Photometrie_Geometrische_Optik.pdf}}
  \label{polar}
\end{figure}\vskip 3pt
As a reminder, polar profiles map each angle $\varphi$ a magnitude $r$ forming a function $r(\varphi)$. They are circular axis versions of the domain $[0..2\pi]$, with negative magnitudes point reflected by 180 degrees. Thus, they are functions with an angular domain making them directionally dependent, which is a well suited representation for point lights, as we use them in a style of Dachsbacher et al. \cite{dachsbacher}. For the sake of interpretability, we exclude negative values (energies) from the scope of our calculations which we express through mathematical clip functions, limiting negative values to $0.0$, which we denote by subscript $+$ in the following. As a start-up thinker for the propagation scheme, we will think of a grid cell in 2D as a center pixel within an 8-neighborhood. Remember, that all considerations from now on are given concerning a single grid cell respectively. It has 8 (4 faces/edges and 4 diagonals) unique neighbors, which are adjacent point lights in the grid (the type of light source with theoretically no finite extend). We consider one face neighbor (top) to shortly explain the steps of the scheme. The diagonals and the others are obtained from derivation and symmetry.

Each cone (yellow and green) is an individual neighbor-dependent angular area. The diagonals take in a greater angular domain while they are located at greater distance and thus need to be attenuated more strongly (consider an isotropic stimulus). We aim for distributing contributions for overlapping cones to transmit attenuated (because of the larger factor $\sqrt{2}$ distance) intensity in form of a shared part to the diagonals in a single step (which also prevents from zigzagging diagonal intensities in case we would transmit diagonal intensities around the corner). Therefore, the intensity gathered in polar coordinates in areas marked in green, needs to be partitioned between 2 of the 8 cone index neighbors with following considerations:

@@

Remark, that we can precompute these linear combination weights and reutilize them in each iteration. We define the contributions as follows:
\begin{align}
	\Phi_{\alpha} &= \varepsilon_1(\int_{-\pi/4}^{-\beta}{I}(\omega)\mathop{d\omega}+\int_{\beta}^{\pi/4}{I}(\omega)\mathop{d\omega})+\int_{-\alpha/2}^{\alpha/2}{I}(\omega)\mathop{d\omega}\\
	\Phi_{\beta} &= \varepsilon_2\int_{-\beta}^{\beta}{I}(\omega)\mathop{d\omega}
\end{align}

@@

\begin{align}
	\Phi_{t,\alpha} &= \int_{-\pi/4}^{\pi/4}{T}(\omega){I}(\omega)\mathop{d\omega}\\
	\Phi_{t,\beta} &= \int_{-\beta}^{\beta}{T}(\omega){I}(\omega)\mathop{d\omega}
\end{align}

@@

\begin{align}
	{\Phi}_t(\omega) &= n_f{T}(\omega){I}(\omega) \hskip 30pt \mathop{w.} \ n_f = \frac{\mean{T}\mean{I}}{\overline{TI}}.
\end{align}

This transforms our equation for the radiant flux into:
\begin{align}
	\Phi_{t,i,\alpha} &= {I}_{t,i}(\omega) = n_f\int_{-\pi/4}^{\pi/4}{T}_i(\omega{I}_{i}(\omega))\mathop{d\omega}\\
	\Phi_{t,i,\beta} &= {I}_{t,i}(\omega) = n_f\int_{-\beta}^{\beta}{T}_i(\omega){I}_{i}(\omega)\mathop{d\omega}.
\end{align}
Which is now respecting energy conservation principles very conveniently, as all we need is a set of means and we are done. This collapses our abstract mathematical operator $\mathop{propagate}$, which is applied to each cell, into the following steps:
\begin{enumerate}
	\item Computation of normalization factor $n_f$
	\item Direction (component)-wise weighting to account for shared part in diagonal cones
	\item Integration (accumulation) total radiant flux weighted with \underline{normalized} transmission profiles inside the angular neighbor range (read-access)
	\item Scaling of cosine lobe corresponding to neighbor direction and subsequent placing to corresponding neighbor (write-access)

@@

\section{Behaviour for Total Anisotropy}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda_1>0$ and the other $\lambda_2=0$) incorporated. For this we set up bidirectional delta-pulses as glyphs to have the whole energy transmitted in just one, discrete direction.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy.png}
    \label{b)}
  \end{minipage}
\caption{a) tensor field Lines and glyphs for ``rings''-Testfield, b) intensity propagation in grid}
\label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as the approach uses 8 discrete directions to propagate averaged intensity whereas the circle uses much more (namely infinite). Hence, the energy can never follow a perfect circle, but at best an 8-edged octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter/escape each) as observable in Fig. \ref{anisotropy}.
\section{Energy Conservation Test}
\label{sect:conserve}
The Energy Conservation Test was done in similar manner as the Propagation Attenuation Test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for about 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum in iteration 0 in absolute values. This approach yields the following graph:

@@

\section{Light transport gradient (LTG)}
The light transport gradient approach, which is closely related to the FTLE approach in vector fields is evaluated from simple ground truth examples to elaborate real datasets.
As a little warmup, we will have an experiment exhibting bare, raw tensor field lines diverging w.r.t. one axis.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/drain(alt)-TFL.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/ftle_drain_alt.png}
    \label{b)}
  \end{minipage}
\caption{a) tensor field lines and glyphs for ``drain'' test field, b) LTG($90^\circ$) for a)}
\label{anisotropy}
\end{figure}
What we can observe here, is called a ``ridge'' occuring as a high value line segment (red vertical track) with edges amplified by a gradient filter. These ridges represent ROIs with underlying Lagrangian coherent structures, which we already discussed in sect. \ref{sect:motiv}. It could for example represent a stress field inside of a mechanical tool.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/inverse-TFL.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/inverse-FTLE-raw.png}
    \label{b)}
  \end{minipage}
\caption{a) tensor field lines and glyphs for ``inverse''-test field, b) LTG($90^\circ$) for a)}
\label{anisotropy}
\end{figure}

We also evaluated the approach for the ``inverse'', whereas we can observe height ridges for the $90^\circ$ slice in any position with diverging tensor field lines w.r.t. the light source direction. This is certainly not the case in the upper ridge whereas tensor field lines converge with respect to the UP ($90^\circ$) direction. This proves that the method is capable of detecting ridges orthogonal to the light source direction, but not in antiparallel directions, which exhibit converging tensor field lines as bidirectional counterpart. Luckily, we measured the gradient for every possible sampled light source direction which complements this information into another slice.

\section{temp}
Der Aufbau dieses Kapitels oder dessen Aufteilung in zwei Kapiteln ist
stark von dem Thema und der Bearbeitung des Themas
abhängig. Beschrieben werden hier Daten, die für eine Evaluation
verwendet wird (Quellen, Beispiele, Statistiken), die Zielsetzung der Evaluation
und die verwendeten Maße sowie die Ergebnisse (u.a.~mithilfe von
Charts, Diagrammen, Abbildungen etc.)

Dieses Kapitel kann auch mit einer Beschreibung der Realisierung eines
Systems beginnen (kein Quellcode, maximal Klassendiagramme!).

>>>>

This chapter will summarize the main contributions of this work studied and state targeted aims and goals as a first step in sect. \ref{sec:overview}. Then we will have a short introduction to the implemented global illumination scheme derived and simplified from an nVidia global illumination approach in sect. \ref{sec:scheme}. Last, we will state the effectively implemented Visualization methods light transport visualization (propagation scheme) and light transport gradient proposed as the main innovatively invented tensor visualization techniques.

@@

\section{Requirements and Ambitions}
\label{sec:spec} 
Our ambition is to motivate a simple and efficient global illumination propagation scheme able to distribute energy profiles in discrete polar form in 2D/3D-space w.r.t. energy conservation and propagation attenuation principles. We then generate transmission profiles from the eigensystems (principal component frames) of the tensors for each cell in the domain (field). This step is done, to provide an orientation for a grid of crystal fibre structures (cf. optical fibres) to redirect the intensities in analogy to the anisotropies of the tensor field within a glyph representation, obtained from Principal Component Analysis. Our approach should be implicitly adaptive to any kind of 2D dataset or slices of 3D datasets. Thus, we require it to be compatible to handle any kind of matrix (symm./anti-symm.) and any kind of resolution of the field (fully-adaptive). At last, our ambition is to segment key locations (LCS/ridges) in the field with tensor field lines (hyperstreamlines) converging/diverging, which is necessarily the same (for bidirectional eigenvectors/singular vectors of tensors). Thus, we aim to generate a new FTLE-related method for tensor field visualization by applying a light transport gradient to the resulting light distributions for every possible position and direction of the light source in the grid generated by stimulation with Dirac-pulses. Our approach should efficiently handle (relatively) large datasets with reasonable resolutions, which turns out to be possible with additional computing power empowered by a cluster. 
%Knapp zwei Seiten, in dem die Anforderungen, die Zielsetzung und die
%Methoden überblicksartig beschrieben werden. Hier sollte die
%Beschreibung ``technischer'' bzw.~``formaler'' sein als in der
%Einleitung, da der Leser nun mit den Grundlagen und verwandten
%Arbeiten vertraut ist.

\section{Light Transport (Propagation) Scheme}
\label{sec:scheme}
As already mentioned, we will motivate a light transport propagation scheme designed to efficiently propagate initial intensity profiles stored in polar coordinates given as symbolic impulses (stimuli) by the user or the config. This polar profiles are first sampled into a vector with elements ranging over the interval $[0,2\pi]$. Polar profiles for different light sources are shown in Fig. \ref{polar}.
\begin{figure}[!t]
  \centering
 {
    \includegraphics[width=0.8\textwidth]
    {img/strahler.png}
  }
  \caption{Polar profiles for different types of emitters ($m=0$: spherical emitter, $m=1$: Lambert emitter, $m=2$: cone emitter}
  \captionsetup{font={footnotesize,bf,it}}
  \caption*{src: \url{http://www.optik.uni-erlangen.de/odem/vorlesung/ws1213/Photometrie_Geometrische_Optik.pdf}}
  \label{polar}
\end{figure}\vskip 3pt
As a reminder, polar profiles map each angle $\varphi$ a magnitude $r$ forming a function $r(\phi)$. They are circular axis versions of the domain $[0..2\pi]$, with negative magnitudes point reflected by 180 degrees. Thus, they are functions with an angular domain making them directionally dependent, which is a well suited representation for point lights, as we use them in a style of Dachsbacher et al. \cite{dachsbacher}. For the sake of interpretability, we exclude negative values (energies) from the scope of our calculations which we express through mathematical clip functions, limiting negative values to $0.0$, which we denote by subscript $+$ in the following. We will describe the emission charactersitics of point lights through such polar functions. Our grid consists of $\mathop{dim}=\mathop{width}\cdot \mathop{height}$ virtual point lights. As a start-up thinker for the propagation scheme, we will think of a grid cell in 2D as a center pixel within an 8-neighborhood with a previously injected point light. Inside of this cell, we imagine a polar profile of radiant intensities for every angle $\omega$. Remember, that all considerations from now on are given concerning a single grid cell respectively. It has 8 (4 faces/edges and 4 diagonals) unique neighbors, which are adjacent point lights in the grid (the type of light source with theoretically no finite extend). We consider one face neighbor (top) to shortly explain the steps of the scheme. The diagonals and the others are obtained from derivation and symmetry.

Each cone type (yellow and green) is an individual neighbor-dependent angular area. The diagonals take in a greater angular domain while they are located at greater distance and thus need to be attenuated more strongly (consider an isotropic stimulus). We aim for distributing contributions for overlapping cones to transmit attenuated (because of the larger factor $\sqrt{2}$ distance) intensity in form of a shared part to the diagonals in a single step (which also prevents from zigzagging diagonal intensities in case we would transmit diagonal intensities around the corner). Therefore, the intensity gathered in polar coordinates in areas marked in green, needs to be partitioned between 2 of the 8 cone index neighbors with following considerations:

@@

Remark, that we can precompute these linear combination weights and reutilize them in each iteration. We define the contributions as follows:
\begin{align}
	\Phi_{\alpha} &= \varepsilon_1(\int_{-\pi/4}^{-\alpha/2}{I}(\omega)\mathop{d\omega}+\int_{\alpha/2}^{\pi/4}{I}(\omega)\mathop{d\omega})+\int_{-\alpha/2}^{\alpha/2}{I}(\omega)\mathop{d\omega}\\
	\Phi_{\beta} &= \varepsilon_2\int_{-\beta}^{\beta}{I}(\omega)\mathop{d\omega}
\end{align}

@@

\begin{align}
	\Phi_{\alpha} &= \varepsilon_1(\int_{-\pi/4}^{-\alpha/2}{T}(\omega){I}(\omega)\mathop{d\omega}+\int_{\alpha/2}^{\pi/4}{T}(\omega){I}(\omega)\mathop{d\omega})+\int_{-\alpha/2}^{\alpha/2}{T}(\omega){I}(\omega)\mathop{d\omega}\\
	\Phi_{\beta} &= \varepsilon_2\int_{-\beta}^{\beta}{T}(\omega){I}(\omega)\mathop{d\omega}
\end{align}

@@

\begin{align}
	{I}_t(\omega) &= n_f{T}(\omega){I}(\omega) \hskip 30pt \mathop{w.} \ n_f = \frac{\mean{T}\mean{I}}{\overline{TI}}.
\end{align}

This transforms our equation for the transmitted radiant flux into:
\begin{align}
	\Phi_{t,i,\alpha} &= {I}_{t,i}(\omega) = n_f\Phi_{\alpha,i}\\
	\Phi_{t,i,\beta} &= {I}_{t,i}(\omega) = n_f\Phi_{\beta,i}.
\end{align}
Which is now respecting energy conservation principles very conveniently, as all we need is a set of means and we are done. This collapses our abstract mathematical operator $\mathop{propagate}$, which is applied to each cell, into the following steps:
\begin{enumerate}
	\item Computation of normalization factor $n_f$
	\item Direction (component)-wise weighting to account for shared part in diagonal cones
	\item Integration (accumulation) total radiant flux weighted with \underline{normalized} transmission profiles inside the angular neighbor range (read-access)
	\item Scaling of cosine lobe corresponding to neighbor direction and subsequent placing to corresponding neighbor (write-access)

@@

\section{Behaviour for Total Anisotropy}
We also wanted to check for the limitations of the approach by having total linear anisotropy (the case whereas one eigenvalue $\lambda_1>0$ and the other $\lambda_2=0$) incorporated. For this we set up bidirectional delta-pulses as transmission profiles to have the whole energy transmitted in just one, discrete direction.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/total_anisotropy.png}
    \label{b)}
  \end{minipage}
\caption{a) tensor field Lines and glyphs for ``rings''-Testfield, b) intensity propagation in grid}
\label{anisotropy}
\end{figure}
What we can observe here, is kind of a sampling drift as the approach uses 8 discrete directions to propagate averaged intensity whereas the circle uses much more (namely infinite if presumed as perfect circle). Hence, the energy can never follow a perfect circle, but at best an 8-edged octagon. This means, that there is a drift of at least two cells per diagonal (one overshoot per enter and escape each) as observable in Fig. \ref{anisotropy}. Nonetheless, the energies are transmitted in circular orbits around the circle center.	
\section{Energy Conservation Test}
\label{sect:conserve}
The Energy Conservation Test was done in similar manner as the Propagation Attenuation Test in sect. \ref{sec:att}. We measure the impulse response of the algorithm for about 80 iterations by summing the total energy in the grid after each iteration and comparing it to the initial energy sum in iteration 0 in absolute values. This approach yields the following graph:

@@

\section{Light transport gradient (LTG)}
The light transport gradient approach, which is closely related to the FTLE approach in vector fields, is evaluated from simple ground truth examples to elaborate real datasets.
As a little warmup, we will have an experiment exhibting bare, raw tensor field lines diverging w.r.t. one axis.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}\bigskip
    \includegraphics[width=\textwidth]{img/drain(alt)-TFL.png}
    \label{a)}
    \caption{a) TFLs and glyphs for ``drain'' test field}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/ftle_drain_alt.png}
    \label{b)}
    \caption{b) LTG($90^\circ$) for a)}
  \end{minipage}
\label{anisotropy}
\end{figure}
What we can observe here, is called a ``ridge'' occuring as a high value line segment (red vertical track) which is already quite obvious for human vision. A gradient filter could be applied to extract and emphasize edges from the image as a preprocessing step for computer vision. These ridges represent ROIs with underlying Lagrangian coherent structures, which we already discussed in sect. \ref{sect:motiv}. It could for example represent a stress field inside of a mechanical tool with a central axis with maximum stress condensation.

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/inverse-TFL.png}
    \label{a)}
    \caption{a) TFLs and glyphs for ``inverse''-test field}
  \end{minipage}
  \begin{minipage}[!t]{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/inverse-FTLE-raw.png}
    \label{b)}
    \caption{b) LTG($90^\circ$) for a)}
  \end{minipage}
\label{anisotropy}
\end{figure}

We also evaluated the approach for the ``inverse'' test field, whereas we can observe height ridges for the $90^\circ$ slice in any position with diverging tensor field lines w.r.t. the light source direction. This is certainly not the case for the upper (missing) ridge whereas tensor field lines converge with respect to the UP ($90^\circ$) direction. This proves that the method is capable of detecting ridges orthogonal to the light source direction, but not in antiparallel directions, which exhibit converging tensor field lines as bidirectional counterpart. Luckily, we measured the gradient for every possible sampled light source direction which complements this information into another slice (and the resulting volume of stacked slices). As we are also interested in the whole ensemble of directions, we can use a volume or surface representation for the $n+1=3$-dimensional grid which results from our FTLE computation. As a subsequent step, we segment height ridges as thresholded volumes from the whole volume grid. The volume grid is what we call the final footprint of the tensor field which is necessarily derived from the initial glyph footprint. From it, we can observe the behavior of the tensor field for any direction. We consider extracted subsets of the volume grid as 3d height ridges in the domain of $\omega$. That is, the slices we observed are stacked along the $z$-axis in the following:

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/inverse_isovolum2.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/inverse_isovolume.png}
    \label{b)}
  \end{minipage}
   \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/inverse_contour.png}
    \label{b)}
  \end{minipage}
    \caption{IsoVolume Filter on LTG volume representation: ``inverse'' test field}
\label{inverse_contour}
\end{figure}
Note that the $z$-axis represents the light source direction angle $\omega$ in this case. The contour filter reveals the star-shaped structure of the tensor field which rotates along the angle axis. This is the effect we already captured for the single slice: For each axis direction we can detect ridges in parallel and orthogonal to our predefined stimulus (light source) direction, but not in antiparallel direction. This causes the star shape to miss one branch or ray which is in turn the antiparallel direction missing for each light source direction emphasizing the impression of rotation. We can also try to segment height ridges represented as surfaces from the resulting volume grids as depicted in Fig \ref{inverse_surface}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[height=\textwidth]{img/inverse_surface.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[height=\textwidth]{img/inverse-wireframe.PNG}
    \label{b)}
  \end{minipage}
    \caption{Contour filter on LTG stacked slice surface representations: ``inverse'' test field}
\label{inverse_surface}
\end{figure}

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=\textwidth]{img/drain_top.PNG}\vskip 10pt
    \includegraphics[width=\textwidth]{img/drain_alt-profile.PNG}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[height=\textwidth]{img/drain_alt_isovolume.PNG}
    \label{b)}
  \end{minipage}
    \caption{Contour filter on LTG stacked slice surface representations: ``inverse'' test field}
\label{inverse_surface}
\end{figure}
